TBD

### 2021-03-10 outputs/paper/paper.Rmd
t_test update

```{r}
#video vs control
t1_a<-t.test(na.omit(dat$post_favor_Sanders[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Sanders[dat$treat_control == 1]))

@@

### T test2
```{r}
#video vs text
t2_a<-t.test(na.omit(dat$post_favor_Sanders[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Sanders[dat$treat_fake_text == 1]))

@@

m2_a%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    AVG_affect_video=estimate1,
    AVG_affect_text=estimate2
  )%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs text")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%# use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```
### T test3
```{r}
#video vs audio
t3_a<-t.test(na.omit(dat$post_favor_Sanders[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Sanders[dat$treat_fake_audio == 1]))

@@

m3_a%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    AVG_affect_video=estimate1,
    AVG_affect_audio=estimate2
  )%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs audio")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%# use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```
### T test 4
```{r}
#video vs skit
t4_a<-t.test(na.omit(dat$post_favor_Sanders[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Sanders[dat$treat_skit == 1]))

>>>>

```{r}
#video vs control
t1_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_control == 1]))

@@

### T test2
```{r}
#video vs text
t2_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_fake_text == 1]))

@@

m2_a%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    AVG_affect_video=estimate1,
    AVG_affect_text=estimate2
  )%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs text")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%# use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```
### T test3
```{r}
#video vs audio
t3_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_fake_audio == 1]))

@@

m3_a%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    AVG_affect_video=estimate1,
    AVG_affect_audio=estimate2
  )%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs audio")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%# use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```
### T test 4
```{r}
#video vs skit
t4_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_skit == 1]))
